---
title: 'Online material for: "Aging of the Exploring Mind: Older Adults Deviate more from Optimality in Complex Choice Environments"'
author: Job J. Schepens
date: "`r format(Sys.time(), '%d %B %Y')`"
graphics: yes
output:
  pdf_document:
    toc: yes
    toc_depth: 5
    highlight: tango
    fig_caption: yes
    fig_height: 4.2
    fig_width: 6.8
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: ../docfiles/mystyle.tex
      after_body: ../docfiles/after_body.tex
  word_document: default
  html_document:
    theme: spacelab
    keep_md: true
    toc: yes
    highlight: haddock
csl: ../docfiles/nature.csl
bibliography: ../docfiles/arc.bib
documentclass: article
fontsize: 11pt
geometry: margin=1in
lang: eng
---

\newpage


```{r, message=FALSE, results='hide', include=FALSE, echo=F, cache=F, fig.height=5, fig.width=5, dev=c('pdf', 'tiff'), dev.args=list(pdf = list(colormodel = 'cmyk'), tiff = list(compression = 'lzw'))}
# pygments (the default), kate, monochrome, espresso, zenburn, haddock, and tango.

knitr::opts_chunk$set(results='markup', cache=T, autodep=T, warning=F, message=F, prompt=F, eval=T, dpi=300, echo=T)

# rmarkdown::render("feedback-dynamic.Rmd", "pdf_document", clean = FALSE)

rm(list=ls())

rmd = "/rmd"
dataloc = "/finaldata"
var = 'C:/Users/schepens/Google Drive' # fu
var = 'C:/Users/Job Schepens/Google Drive' # fu laptop
const = '/ownCloud/Experiments/feedback and dynamic/github/Bandit'
home = paste(var, const, sep='')
wd = paste(home, rmd, sep='')
setwd(wd)

# home <- getwd()
# setwd(paste(home,rmd, sep = ""))

pointsize = 7
cm_width = 1 * 8.3   # max width for 1 column figures
cm_width = 1 * 13
golden_ratio = (1 + sqrt(5)) / 2
# golden_ratio = 1
# square = 1.3
# square = .6
square = 1
cm_height = square * cm_width / golden_ratio
cm_to_inch = 2.54
inch_width = cm_width/cm_to_inch
inch_height = cm_height/cm_to_inch

# options(width=60, width.cutoff=60)
# install.packages("combinat")
library(knitr)
library(lattice)
library(effects)
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(stargazer)
library(psych)
library(png)
library(combinat)
library(forcats)
theme_set(theme_bw())
```

\newpage


# Behavorial analysis

```{r child = 'exp1-finaldata.Rmd'}
```

\newpage


```{r child = 'exp1-finaldata-evplots.Rmd'}
```

\newpage


```{r child = 'exp1-finaldata-expplots.Rmd'}
```

\cleardoublepage


```{r child = 'exp1-finaldata-regret.Rmd'}
```

\newpage




# Optimality models

```{r child = 'exp1-finaldata-fit.Rmd'}
```

\newpage


```{r child = 'exp1-viscomp.Rmd'}
```

\newpage


# Individual plots

```{r child = 'exp1-finaldata-exploratory.Rmd'}
```

\newpage


# Acknowledgements

The manuscript has been automatically generated with 
[R](http://r-project.org/)
using 
[Markdown](http://daringfireball.net/projects/markdown/) (for word processing), 
[`knitr`](http://yihui.name/knitr/) (for putting evaluated r code into markdown), 
[`pandoc`](http://johnmacfarlane.net/pandoc/) (for converting to latex, html, and docx), and 
[MiKTeX](http://miktex.org/) (for converting latex to pdf).

\newpage


# Session info

```{r, echo=FALSE, results="asis"}
sessionInfo()
```

```{r, cache=F, include=FALSE, }
opts_chunk$set(include=FALSE)
opts_chunk$set(eval=FALSE)
```

# References